RUPEE: A fast and accurate purely geometric protein structure search

### 2019-01-29 docs/rupee_2.tex
bib

\section*{Related Work}

@@

Taken together, \figurename~\ref{fig:combined_scoring_tm_avg} and \figurename~\ref{fig:combined_scoring_tm_q} show that the results of RUPEE and mTM are roughly equal and where they do differ is a result of the differences in normalization.

@@

\section*{Supporting Information}

@@

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
%

\nocite{Ayoub2017}
\nocite{BioJava2012}
\bibliography{rupee_2}

>>>>

\section*{Related work}

@@

Taken together, Figs~\ref{fig:combined_scoring_tm_avg}~and~\ref{fig:combined_scoring_tm_q} show that the results of RUPEE and mTM are roughly equal and where they do differ is a result of the differences in normalization.

@@

\section*{Supporting information}

@@

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{Crick1970}
Crick F.
\newblock Central dogma of molecular biology.
\newblock Nature. 1970;227(5258):561--563.

\bibitem{Fox2013}
Fox NK, Brenner SE, Chandonia JM.
\newblock {SCOP}e: Structural Classification of Proteins - extended,
  integrating {SCOP} and {ASTRAL} data and classification of new structures.
\newblock Nucleic Acids Res. 2014;42(1):304--309.

\bibitem{Orengo1997}
Orengo C, Mitchie A, Jones S, Jones DT, Swindells M, Thornton JM.
\newblock {CATH} - A hierarchic classification of protein domain structures.
\newblock Structure. 1997;5(8):1093--1109.

\bibitem{Cheng2014}
Cheng H, Schaeffer RD, Liao Y, Kinch LN, Pei J, Shi S, et~al.
\newblock {ECOD: An Evolutionary Classification of Protein Domains}.
\newblock PLoS Computational Biology. 2014;10(12).

\bibitem{Dong2018}
Dong R, Pan S, Peng Z, Zhang Y, Yang J.
\newblock {mTM-align: a server for fast protein structure database search and
  multiple protein structure alignment}.
\newblock Nucleic Acids Research. 2018;46(July):380--386.

\bibitem{Krissinel2004}
Krissinel E, Henrick K.
\newblock {Secondary-structure matching (SSM), a new tool for fast protein
  structure alignment in three dimensions}.
\newblock Acta Crystallographica Section D: Biological Crystallography.
  2004;60(12 I):2256--2268.

\bibitem{Redfern2007}
Redfern OC, Harrison A, Dallman T, Pearl FMG, Orengo CA.
\newblock {CATHEDRAL}: A Fast and Effective Algorithm to Predict Folds and
  Domain Boundaries from Multidomain Protein Structures.
\newblock {PL}o{S} Comput Biol. 2007;3(11):e232.

\bibitem{Zhang2004}
Zhang Y, Skolnick J.
\newblock Scoring function for automated assessment of protein structure
  template quality.
\newblock Proteins. 2004;57(4):702--710.

\bibitem{Shindyalov1998}
Shindyalov IN, Bourne PE.
\newblock Protein structure alignment by incremental combinatorial extension
  ({CE}) of the optimal path.
\newblock Protein Eng Des Sel. 1998;11(9):739--747.

\bibitem{Ye2003}
Yuzhen~Ye AG.
\newblock Flexible structure alignment by chaining aligned fragment pairs
  allowing twists.
\newblock Bioinformatics. 2003;19(2):246--255.

\bibitem{Zhang2005}
Zhang Y, Skolnick J.
\newblock {TM-align: A protein structure alignment algorithm based on the
  TM-score}.
\newblock Nucleic Acids Research. 2005;33(7):2302--2309.

\bibitem{Sander1995}
Holm L, Sander C.
\newblock Dali: a network tool for protein structure comparison.
\newblock Trends in Biochemical Sciences. 1995;20(11):478 -- 480.

\bibitem{Gilbrat1996}
Gilbrat JF, Madej T, Bryant SH.
\newblock Surprising similarities in structure comparison.
\newblock Curr Opin Struct Biol. 1996;6(3):377--385.

\bibitem{Ye2004}
Yuzhen~Ye AG.
\newblock {FATCAT}: a web server for flexible structure comparison and
  structure similarity searching.
\newblock Nucleic Acids Res. 2004;32(2):582--585.

\bibitem{Prlic2010}
Prli{\'c} A, Bliven S, Rose PW, Bluhm WF, Bizon C, Godzik A, et~al.
\newblock Pre-calculated protein structure alignments at the {RCSB} {PDB}
  website.
\newblock Bioinformatics. 2010;26(23):2983--2985.

\bibitem{Holm2010}
Holm L, Rosenstr{\"{o}}m P.
\newblock {Dali server: Conservation mapping in 3D}.
\newblock Nucleic Acids Research. 2010;38(SUPPL. 2):1--5.

\bibitem{gkw1000}
Rose PW, Prli{\'c} A, Altunkaya A, Bi C, Bradley AR, Christie CH, et~al.
\newblock The {RCSB} protein data bank: integrative view of protein, gene and
  {3D} structural information.
\newblock Nucleic Acids Res. 2017;45(D1):D271--D281.

\bibitem{Carpentier2005}
Carpentier M, Brouillet S, Pothier J.
\newblock {YAKUSA}: A fast structural database scanning method.
\newblock Proteins. 2005;61(1):137--151.

\bibitem{Daniluk2011}
Daniluk P, Lesyng B.
\newblock A novel method to compare protein structures using local descriptors.
\newblock BMC Bioinformatics. 2011;12(1):344.

\bibitem{Ritchie2012}
Mavridis L, Ritchie DW.
\newblock In: {3D-Blast}: {3D} protein structure alignment, comparison, and
  classification using spherical polar fourier correlations. World Scientific;
  2012. p. 281--292.

\bibitem{Ramachandran1968}
Ramachandran GN, Sasisekharan V.
\newblock Conformation of polypeptides and proteins.
\newblock Adv Protein Chem. 1968;23:283--438.

\bibitem{Karplus2010}
Hollingsworth SA, Karplus PA.
\newblock A fresh look at the {R}amachandran plot and the occurrence of
  standard structures in proteins.
\newblock Biomol Concepts. 2010;1:271--283.

\bibitem{Kabsch1983}
Kabsch W, Sander C.
\newblock Dictionary of protein secondary structure: Pattern recognition of
  hydrogen-bonded and geometrical features.
\newblock Biopolymers. 1983;22(12):2577--2637.

\bibitem{Aungand2004}
Aungand Z, Tan KL.
\newblock Rapid 3D protein structure database searching using information
  retrieval techniques.
\newblock Bioinformatics. 2004;20(7):1045--1052.

\bibitem{Zhang2010}
Zhang L, Bailey J, Konagurthu AS, Ramamohanarao K.
\newblock A fast indexing approach for protein structure comparison.
\newblock {BMC} Bioinformatics. 2010;11(Suppl 1):S46.

\bibitem{Budowski2010}
Budowski-Tal I, Nov Y, Kolodny R.
\newblock {FragBag}, an accurate representation of protein structure, retrieves
  structural neighbors from the entire {PDB} quickly and accurately.
\newblock Proceedings of the National Academy of Sciences.
  2010;107(8):3481--3486.

\bibitem{Broder1997a}
Broder AZ.
\newblock On the resemblance and containment of documents.
\newblock In: Proc. Compression and Complexity of Sequences. Positano, Italy;
  1997. p. 21--29.

\bibitem{Karp1987}
Karp RM, Rabin MO.
\newblock Efficient randomized pattern-matching algorithms.
\newblock {IBM} Journal of Research and Development. 1987;31(2):249--260.

\bibitem{Levan1971}
Levandowsky M, Winter D.
\newblock Distance between Sets.
\newblock Nature. 1971;234(5323):34--35.

\bibitem{Ayoub2017}
Ayoub R, Lee Y.
\newblock RUPEE: Scalable protein structure search using run position encoded
  residue descriptors.
\newblock In: 2017 IEEE International Conference on Bioinformatics and
  Biomedicine (BIBM); 2017. p. 74--78.

\bibitem{Broder1997b}
Broder AZ, Glassman SC, Manasse MS, Zweig G.
\newblock Syntactic clustering of the Web.
\newblock Computer Networks and ISDN Systems. 1997;29(8-13):1157--1166.

\bibitem{Joshi2008}
Joshi S, Contractor D, Ng K, Deshpande PM, Hampp T.
\newblock Auto-grouping emails for faster e-discovery.
\newblock In: Proceedings of Very Large Databases Endowment 2011. vol.~4; 2011.
  p. 1284--1294.

\bibitem{Broder1998}
Broder AZ, Charikar M, Frieze AM, Mitzenmacher M.
\newblock Min-wise independent permutations.
\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
  327--336.

\bibitem{Indyk1998}
Indyk P, Motwani R.
\newblock Approximate nearest neighbors: towards removing the curse of
  dimensionality.
\newblock In: ACM Symposium on Theory of Computing. Dallas, USA; 1998. p.
  604--613.

\bibitem{Rajaraman2012}
Rajaraman A, Ullman JD.
\newblock 3.
\newblock In: Mining of Massive Datasets. Cambridge University Press; 2012. p.
  53--70.

\bibitem{Xu2010}
J~Xu YZ.
\newblock How significant is a protein structure similarity with {TM}-score =
  0.5?
\newblock Bioinformatics. 2010;26(7):889--895.

\bibitem{Andreeva2007}
Andreeva A, Prli{\'c} A, Hubbard TJP, Murzin AG.
\newblock {SISYPHUS}: structural alignments for proteins with non-trivial
  relationships.
\newblock Nucleic Acids Res. 2007;35(1):253--259.

\bibitem{BioJava2012}
Prli{\'c} A, Yates A, Bliven SE, Rose PW, Jacobsen J, Troshin PV, et~al.
\newblock Bio{J}ava: an open-source framework for bioinformatics in 2012.
\newblock Bioinformatics. 2012;28(20):2693--2695.

\end{thebibliography}
